Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-31 PandaOverview.tex
Record comments and changes from Danila

>>>>

\mtnote{DDM: just enacts decisions about registering files into datasets. These
decisions are made by productions. DDM DOES OT DECIDE which file should be in
which dataset.}
\mtnote{No communication between APF and PanDA Server (deleted arrow, adjust
numbers and related text)}
\mtnote{No more DDM Service on Edge on grid sites. DDM directly interacts with
SE (deleted arrows, moved number 8. Update labels and related text)}
